---
title: "chatGPT 데이터셋"
description: "chatGPT가 추천한 데이터 과학 적합한 데이터셋으로 학습을 전개합니다."
date: today # 날짜 설정: now, last-modified
author:
  - name: 이광춘
    affiliation: TCS
title-block-banner: false
format:
  html:
    css: css/quarto-fonts.css
    code-fold: false
    toc: true
    toc-depth: 2
    number-sections: true
    highlight-style: github    
    self-contained: false
bibliography: bibliography.bib
link-citations: yes
csl: apa-single-spaced.csl
editor_options: 
  chunk_output_type: console
---

OpenAI에서 최근에 공개한 [chatGPT](https://openai.com/blog/chatgpt/)와 함께 인공지능과 공존할 수 있는 방법을 모색해 봅니다.

# 회귀모형

::: {.callout-caution collapse="true"}
## what is the best dataset for regression?

There is no one "best" dataset for regression, as the appropriate dataset will depend on the specific problem you are trying to solve. Some common datasets that are often used for regression include the **Boston Housing dataset**, the **California Housing dataset**, and the **Diabetes dataset**. These datasets are well-studied and can be easily accessed by researchers, making them a good starting point for many regression tasks. Ultimately, the best dataset for your regression problem will depend on the specific problem you are trying to solve and the nature of the data you have available.
:::

::: {.callout-caution collapse="true"}
## how about mpg dataset?

The mpg dataset is a dataset that contains information on the fuel efficiency of different cars. It is commonly used in regression tasks, as the goal is often to predict **a car's fuel efficiency** based on various features such as its engine size and horsepower. This dataset can be a good choice for regression tasks, as it contains a large number of records and a variety of features that can be used to train a regression model. However, as with any dataset, it's important to carefully evaluate the quality and relevance of the data before using it for your specific task.
:::

::: {.callout-caution collapse="true"}
## can you show me a sample code with R?

Sure, here is a simple example of a linear regression model in R:

```{r}
#| eval: true
#| warning: false
#| message: false
#| class-output: output

# Load the necessary libraries
library(tidyverse)

# Load the mpg dataset
data("mpg")

# Fit a linear regression model using the "displ" and "hwy" variables
model <- lm(hwy ~ displ, data = mpg)

# Print the model summary
summary(model)

# Predict the hwy fuel efficiency for a car with a displacement of 3
predict(model, newdata = data.frame(displ = 3))

```

This code fits a linear regression model using the displ and hwy variables from the mpg dataset, and then uses the model to predict the fuel efficiency of a car with a displacement of 3. Note that this is a very simple example, and there are many different ways to perform regression in R. For more information and examples, you can refer to the R documentation and tutorials on regression.
:::

# 분류모형

::: {.callout-caution collapse="true"}
## I am learning machine learning. In particular I'd like to build classification model. Could you recommend a suitable dataset for this purpose?

Sure, there are many datasets that you can use to build a classification model. One good dataset to start with is the **Iris dataset**, which is a popular dataset used in machine learning examples. It contains data on the different species of iris flowers, including their petal and sepal length and width. This dataset is small, so it's easy to work with, but it's also complex enough to provide a good challenge for a classification model. Other datasets that you might consider include the **MNIST dataset** for handwritten digit recognition, the **CIFAR-10 dataset** for object recognition, and the **IMDB dataset** for sentiment analysis. Ultimately, the best dataset for you to use will depend on your specific goals and needs.
:::

::: {.callout-caution collapse="true"}
## Can you show me sample python code for building classification machine learning model?

Here is an example of how you might build a simple classification model using Python:

```{python}
#| eval: false
# Import the necessary libraries
import numpy as np
from sklearn import datasets
from sklearn.model_selection import train_test_split
from sklearn.linear_model import LogisticRegression

# Load the iris dataset
iris = datasets.load_iris()

# Split the data into features and labels
X = iris.data
y = iris.target

# Split the data into training and test sets
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2)

# Create a logistic regression model
model = LogisticRegression()

# Train the model on the training data
model.fit(X_train, y_train)

# Evaluate the model on the test data
score = model.score(X_test, y_test)

# Print the accuracy of the model
print("Accuracy:", score)
```

This code creates a logistic regression model and trains it on the Iris dataset. It then evaluates the model on the test data and prints the model's accuracy. This is just one example of how you might build a classification model using Python -- there are many other algorithms and approaches that you can use.
:::

::: {.callout-caution collapse="true"}
## Can you translate the python code above into R code with tidymodels?

Sure, here is an example of how you might translate the Python code above into R code using the tidymodels package:

```{r}
#| error: true
#| warning: false
# Install and load the tidymodels package
# install.packages("tidymodels")
library(tidymodels)

# Load the iris dataset
iris <- datasets::iris

# Split the data into features and labels
X <- iris %>% select(-Species)
y <- iris %>% pull(Species)

# Split the data into training and test sets
splits <- initial_split(iris, prop = 0.8)

# Preprocess the data using recipe
rec <- recipe(Species ~ ., data = iris) %>%
  step_zv(all_predictors()) %>%
  step_dummy(all_nominal(), -all_outcomes())

# Create a logistic regression model
lr_mod <- logistic_reg() %>%
  set_engine("glm") 

# Train the model on the training data
lr_fit <- lr_mod %>%
  fit(rec, data = training(splits))

# Evaluate the model on the test data
lr_pred <- lr_fit %>%
  predict(new_data = testing(splits))

# Print the accuracy of the model
lr_pred %>% metrics(truth = testing(splits) %>% pull(Species), estimate = .pred_class) %>%
  metric_set(acc)
```

This code uses the tidymodels package to create a logistic regression model and train it on the Iris dataset. It then evaluates the model on the test data and prints the model's accuracy. This is just one example of how you might build a classification model using `tidymodels` -- there are many other algorithms and approaches that you can use.
:::

# 차원축소

::: {.callout-caution collapse="true"}
## I'd like to practice multivariate data analysis. In particular I am interested in principal component analysis. Can you recommend a dataset for this purpose?

Sure! There are many publicly available datasets that would be suitable for practicing principal component analysis. One example is the Iris dataset, which is a well-known dataset in the field of statistics and machine learning. It contains 150 samples of iris flowers, with each sample having four measurements: sepal length, sepal width, petal length, and petal width. These measurements are used to classify the iris flowers into three different species: Iris setosa, Iris virginica, and Iris versicolor.
:::

::: {.callout-caution collapse="true"}
## Already I used the Iris data. Can you recommend another dataset, something interesting?

Sure! Here are a few other publicly available datasets that you could use for practicing principal component analysis:

-   The Wine dataset, which contains chemical analysis of 13 different wines grown in the same region in Italy. This dataset can be used to classify the wines based on their chemical properties.
-   The MNIST dataset, which contains images of handwritten digits. This dataset can be used to classify the digits based on their visual appearance.
-   The Human Activity Recognition dataset, which contains sensor readings from smartphones worn by 30 different subjects performing six different activities. This dataset can be used to classify the activities based on the sensor readings.

These are just a few examples - there are many other publicly available datasets that you could use for practicing principal component analysis. You can find many more by searching online for "multivariate datasets" or "principal component analysis datasets."
:::

::: {.callout-caution collapse="true"}
## show me a sample R code for the Wine dataset.

Here is a sample R code that you could use to perform principal component analysis on the Wine dataset:

```{r}
#| eval: false
# Load the wine dataset
data <- read.csv("wine.csv")

# Perform principal component analysis
pca <- prcomp(data, scale = TRUE)

# Print the results
print(pca)

```
:::

# SQL 데이터베이스

::: {.callout-caution collapse="true"}
## What is the best dataset for learning SQL?

There are many datasets that you can use to learn SQL, and the best one for you will depend on your goals and what you want to learn. One option is the **Northwind database**, which is a small, well-known dataset that is often used for learning SQL. It includes data on customers, orders, and products, and you can use it to practice a wide range of SQL queries. Other options include the **AdventureWorks database** and the **Chinook database**, both of which are similar to Northwind and can be used for learning SQL. Ultimately, the best dataset for you to use will depend on your individual learning goals and what you hope to get out of the experience.
:::

::: {.callout-caution collapse="true"}
## I need license free datasets. which one is the best for learning SQL?

If you are looking for license-free datasets for learning SQL, you have several options. One option is the Northwind database, which is a small, well-known dataset that is often used for learning SQL. It includes data on customers, orders, and products, and you can use it to practice a wide range of SQL queries. Other options include the AdventureWorks database and the Chinook database, both of which are similar to Northwind and can be used for learning SQL. Additionally, there are many other free and open datasets available online that you can use for learning SQL. Some websites that offer free datasets include Kaggle, the UCI Machine Learning Repository, and the US government's data.gov website.
:::

::: {.callout-caution collapse="true"}
## Is Northwind dataset really copyright-free?

The Northwind database is **not copyright-free**. It is copyrighted by Microsoft, and its use is subject to the terms of the Microsoft SQL Server Sample License Agreement. However, Microsoft allows users to download and use the Northwind database for **educational and non-commercial purposes**, provided that they comply with the terms of the license agreement. If you want to use the Northwind database for commercial purposes, you will need to obtain a commercial license from Microsoft. It is important to always read and understand the terms of any license agreement before using a dataset for any purpose.
:::

::: {.callout-caution collapse="true"}
## how about DVD rental dataset?

I'm sorry, but I am not able to browse the internet to find information on specific datasets. As a large language model trained by OpenAI, my knowledge is based on the text that I have been trained on, and I do not have the ability to browse the internet or access external information. I can only provide information based on what I have been trained on, which has a fixed cutoff date. In this case, I do not have any information on the DVD rental dataset, as my training data only goes up **until 2021** and I do not have the ability to access or browse external information.
:::

|                          저작권                           |  데이터베이스  |                                                 데이터셋                                                  | 설명                                                                                                                                                                                                                          |
|:---------------------------------------------------------:|:--------------:|:---------------------------------------------------------------------------------------------------------:|-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
|                           상용                            | Microsoft SQL  | [Northwind](https://github.com/microsoft/sql-server-samples/tree/master/samples/databases/northwind-pubs) | The Northwind database contains the sales data for a fictitious company called "Northwind Traders," which imports and exports specialty foods from around the world.                                                          |
|                           상용                            | Microsoft SQL  |       [AdventureWorks](https://github.com/Microsoft/sql-server-samples/releases/tag/adventureworks)       | OLTP database for a fictitious, multinational manufacturing company called **Adventure Works** Cycles                                                                                                                         |
| [CC0](https://creativecommons.org/publicdomain/zero/1.0/) | Northwind 대안 |                          [Chinook](https://github.com/lerocha/chinook-database)                           | digital media store                                                                                                                                                                                                           |
|                           상용                            |  Oracle MySQL  |                              [Sakila](https://dev.mysql.com/doc/sakila/en/)                               | Movie rental database with actors, ratings, payments, etc                                                                                                                                                                     |
|                            BSD                            |   PostgreSQL   |                             [Pagila](https://github.com/devrimgunduz/pagila)                              | **DVD rental store**, containing information about films (like title, category, actresses), rental stores (like address, staff members, customers) and rentals, where a customer rents a film from a store through its staff. |
|                            MIT                            |    SQlite3     |                        [survey](https://swcarpentry.github.io/sql-novice-survey/)                         | Education DB for SQL lesson of the Software Carpentry                                                                                                                                                                         |
|                            MIT                            |    SQlite3     | [Portal Project Teaching](https://figshare.com/articles/dataset/Portal_Project_Teaching_Database/1314459) | Education DB for SQL lesson of the Data Carpentry                                                                                                                                                                             |
|                            ???                            |     duckdb     |                         [release](https://github.com/duckdb/duckdb-data/releases)                         | taxi, job, stock ...                                                                                                                                                                                                          |
